### 2014-04-01 LaTeX/RhodiumEmp.tex
cleaning
Fixed subscripts on equation (I think)
Check this - I added i,t to all the beta subscripts as I believe all
our variables are unit and time varying.  That’s cool, right?

\section{Empirics}
\label{empirics}

\subsection{Data and Sample}

@@

@@

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{t}) \\
	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{t}) \;+\; \beta_{5}(Conflict \; Type_{t}) \\
	& \;+\; \beta_{6}(Conflict \; Duration_{t}) \;+\; \beta_{7}(Inflation_{t-1}) \\
	& \;+\; \beta_{8}(Ln(Land \; Area)_{t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
\end{align*}

\subsection{Results}

>>>>

\section{Data and Sample}
\label{empirics}

\subsection{Conflict and City Data}

@@

\subsection{Level of Aggregation}

@@

\begin{align*}
	\% \Delta GDP_{i,t} &= \beta_{1}(Upper \; Income_{i,t}) \\
	& \;+\; \beta_{2}(Conflict \; Intensity_{i,t}) \;+\; \beta_{3}(Ln(Conflict \; Area)_{i,t}) \\
	& \;+\; \beta_{4}(Ln(Min. \; Conflict \; Dist.)_{i,t}) \;+\; \beta_{5}(Conflict \; Type_{i,t}) \\
	& \;+\; \beta_{6}(Conflict \; Duration_{i,t}) \;+\; \beta_{7}(Inflation_{i,t-1}) \\
	& \;+\; \beta_{8}(Ln(Land \; Area)_{i,t}) \;+\; \alpha_{i} + \gamma_{t} + \mu_{i,t}
\end{align*}

\section{Results}
